Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/splitting.tex
Splitting text tightening.

\paragraph{Tuple.} For an example of splitting terms with more than one argument, consider the tuple $\tup{e_1,e_2}$,
where $\diaone {e_k} {\xi_k} {v_k}$ and $\rtab {\xi_k} {v_k} \vsplito
\mval {i_k} {q_k}$ for $k = 1,2$.  Inductively:
\[
	\splitone {e_k} A {c_k} {l_k.r_k} \text{ and } \reduce {c_k} {\tup{i_k,b_k}} \text{ and } [b_k/l_k]r_k \equiv q_k
\]
Since $\diaone {\tup{e_i,e_2}} {\xi_1,\xi_2} {\tup{v_1,v_2}}$ 
and $\rtab {\xi_1,\xi_2} {\tup{v_1,v_2}} \vsplito \mval {\tup{i_1,i_2}} {\tup{q_1,q_2}}$,
the validity of the split $\splitone {\tup{e_1,e_2}} A {c} {l.r}$ requires,
\[
	\reduce {c} {\tup{\tup{i_1,i_2},b}} \text{ and } [b/l]r \equiv \tup{q_1,q_2}
\]
To satisfy this, our algorithm uses a boundary value which is the tuple of the boundary values of the subexpressions,
$b = \tup{b_1,b_2}$. This is deconstructed with a tuple pattern, $l.r = \tup{l_1,l_2}.\tup{r_1,r_2}$,
and constructed using,
\[
c = \letin{\tup{y_1,z_1}}{c_1}{\letin{\tup{y_2,z_2}}{c_2}{\tup{\tup{y_1, y_2},\tup{z_1, z_2}}}}
\]

>>>>

\paragraph{Tuple.} For an example of splitting terms with more than one argument, consider the tuple $\tup{e_1,e_2}$,
where $\diaone {e_k} {\xi_k} {v_k}$ and $\rtab {\xi_k} {v_k} \vsplito
\mval {i_k} {q_k}$ for $k = 1,2$.  Inductively:
\[
	\splitone {e_k} A {c_k} {l_k.r_k} \text{ and } \reduce {c_k} {\tup{i_k,b_k}} \text{ and } [b_k/l_k]r_k \equiv q_k
\]
Since $\diaone {\tup{e_i,e_2}} {\xi_1,\xi_2} {\tup{v_1,v_2}}$ 
and $\rtab {\xi_1,\xi_2} {\tup{v_1,v_2}} \vsplito \mval {\tup{i_1,i_2}} {\tup{q_1,q_2}}$,
splitting generates:
\[
	\reduce {c} {\tup{\tup{i_1,i_2},b}} \text{ and } [b/l]r \equiv \tup{q_1,q_2}
\]
The resulting boundary value is the tuple of the boundary values of
the subexpressions, $b = \tup{b_1,b_2}$.  The value is 
constructed using,
\[
c = \letin{\tup{y_1,z_1}}{c_1}{\letin{\tup{y_2,z_2}}{c_2}{\tup{\tup{y_1, y_2},\tup{z_1, z_2}}}}
\]
And deconstructed with a tuple pattern, $l.r = \tup{l_1,l_2}.\tup{r_1,r_2}$,
